---
title: ""
output: html_document
---

<!--
Copyright 2019 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Interactive Steps to Set-Up Repository

(1) Open an new, empty repository in your GitHub organization

- choose repo name (follow a style convention if you wish)
- add a 1-sentence description of what is _in_ the repo
- copy URL for repository to clipboard

(2) Clone the repository to your machine

In RStudio:

- select New Project -- Version Control -- paste in URL -- choose location for local copy

Terminal or Git Bash: `git clone <URL for repository>

(3) Auto-populate with files with `bcgovr`


```{r pressure, eval=FALSE}
library(bcgovr) #available from GitHub https://github.com/bcgov/bcgovr

create_bcgov_project(rmarkdown = FALSE) #use a md for readme instead of Rmd
```


